---
title: "p8105_hw1_qra2000"
output: github_document
date: "2023-09-18"
---

## Problem 1

The chunk below loads the necessary libraries: `moderndive` library, the `early_january_weather` dataset, and the `tidyverse` library. 

```{r}
library(moderndive)
library(tidyverse)
```

```{r}
data("early_january_weather")
```


The next chunk describes the `early_january_weather` dataset using the following variables:

*   the size of the dataset (using nrow and ncol)

*   the mean temperature

*   the variables in this dataset, including names / values of important variables


Size of the dataset (using nrow and ncol):
```{r}
early_january_weather

nrow(early_january_weather)

ncol(early_january_weather)
```

The mean temperature:
```{r}
temp <- early_january_weather$temp

mean(temp)
```

The variables in this dataset, including names/values of important variables:

```{r}
class(early_january_weather)

str(early_january_weather)

ls(early_january_weather)
```

The `early_january_weather` dataset shows the characteristics of weather patterns for the Newark Liberty International Airport (EWK) in early January 2013. The `early_january_weather` dataset is a 358 row x 15 row tibble dataset. The mean temperature of the dataset is 39.58212. The variables in this dataset are: origin, year, month, day, hour, temp, dewp, humid, wind_dir, wind_speed, wind_gust, precip, pressure, visib, and time_hour. Note, the origin variable type is a character; year, month, day, and hour are integers. Temp, dewp, humid, wind_dir, wind_speed, wind_gust, precip, pressure, and visib are numerical values. Time_hour is a date/time format.



## Problem 2

The chunk below creates a dataframe comprised of a random sample of size 10 from a standard Normal distribution, a logical vector indicating whether elements of the sample are greater than 0, a character vector of length 10, and a factor vector of length 10, with 3 different factor “levels”.

```{r}
hw1_df = 
  tibble(
    norm_samp = rnorm(10),
    norm_samp_pos = norm_samp > 0)
    character(length = 10)
    factor(x=character(10), levels = 3)
)
```

The mean of the sample is `r mean(pull(hw1_df, norm_samp))`.




















