---
title: "p8105_hw1_qra2000"
output: github_document
date: "2023-09-18"
---

## Problem 1

Load the `moderndive` library and the `early_january_weather` dataset.

```{r}
library(moderndive)
library(tidyverse)
```

```{r}
data("early_january_weather")
```


Next, describe the `early_january_weather` dataset using the following variables:
* the variables in this dataset, including names / values of important variables
* the size of the dataset (using nrow and ncol)
* the mean temperature

Size of the dataset (using nrow and ncol):
```{r}
early_january_weather

nrow(early_january_weather)

ncol(early_january_weather)
```

The mean temperature:
```{r}
temp <- early_january_weather$temp

mean(temp)
```

The variables in this dataset, including names/values of important variables:

```{r}
class(early_january_weather)

str(early_january_weather)

ls(early_january_weather)
```

The `early_january_weather` dataset shows the characteristics of weather patterns for the Newark Liberty International Airport (EWK) in early January 2013. The `early_january_weather` dataset is a 358 row x 15 row tibble dataset. The mean temperature of the dataset is 39.58212. The variables in this dataset are: origin, year, month, day, hour, temp, dewp, humid, wind_dir, wind_speed, wind_gust, precip, pressure, visib, and time_hour. Note, the origin variable type is a character; year, month, day, and hour are integers. Temp, dewp, humid, wind_dir, wind_speed, wind_gust, precip, pressure, and visib are numerical values. Time_hour is a date/time format.



## Problem 2

First, create a data frame comprised of:

* a random sample of size 10 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 10
* a factor vector of length 10, with 3 different factor “levels”

plot_df = 
  tibble(
    x = rnorm(10),
    y = 1 + 2 * x + rnorm(1000)
  )











